Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-08 README.Rmd
small change
added forked ggpcp installation instructions

1. Pull the repository from GitHub.
2. Unzip all .zip files in the repository (`data-bullet-train.csv.zip`, `data-bullet-test.csv.zip`, `data-example-signatures.csv.zip`, and `figure-08-1.png.zip`).
3. Install R packages goodekat/lime and goodekat/limeaid R from GitHub using devtools.

```{r eval = FALSE}
devtools::install_github("goodekat/lime")
devtools::install_github("goodekat/limeaid")
```

@@

**Need to write still**

>>>>

1. Pull the repository from GitHub.
2. Unzip all .zip files in the repository (`data-bullet-train.csv.zip`, `data-bullet-test.csv.zip`, `data-example-signatures.csv.zip`, and `figure-08-1.png.zip`).
3. Install R packages goodekat/lime, goodekat/limeaid, and goodekat/ggpcp from GitHub using devtools. (Note that goodekat/lime and goodekat/ggpcp are forked versions of thomasp85/lime and yaweige/ggpcp, respectively with minor changes to meet the needs of the manuscript.)

```{r eval = FALSE}
devtools::install_github("goodekat/lime")
devtools::install_github("goodekat/limeaid")
devtools::install_github("goodekat/ggpcp")
```

@@

**Need to write...**
